### 2021-03-26 Chapter-3/Chapter-3.tex
update

Existing approach relies on satisfiability modulo theories (SMT) solvers (e.g,
Z3~\cite{DeMoura:2008:ZES:1792734.1792766}) to find satisfying $k_1$ and $k_2$.
We argue that while it is a universal approach to solving constraints with SMT
solvers, for constraints with the above formats, using custom heuristics and
testing is much more efficient in practice. Constraint solving is a decision
problem expressed in logic formulas. SMT solvers transfer the inputted SMT
formula into the boolean conjunctive normal form (CNF) and feed it into the
internal boolean satisfiability problem (SAT) solver. The translation process,
called ``bit blasting'', is time-consuming. Also, as the SAT problem is a
well-known NP-complete problem, it is also hard to deal when it comes to
realistic uses with huge formulas. Despite the rapid development of SMT solvers
in recent years, constraint solving remains one of the obstacles to achieve the
scalability for real-world cryptosystems.

>>>>

Existing approach relies on satisfiability modulo theories (SMT) solvers (e.g,
Z3~\cite{DeMoura:2008:ZES:1792734.1792766}) to find satisfying $k_1$ and $k_2$.
We argue that while it is a universal approach to solving constraints with SMT
solvers, for constraints with the above formats, using custom heuristics and
testing is much more efficient in practice. Constraint solving is a decision
problem expressed in logic formulas. SMT solvers transfer the inputted SMT
formula into the boolean conjunctive normal form (CNF) and feed it into the
internal boolean satisfiability problem (SAT) solver. The translation process,
called ``bit blasting'', is time-consuming. Also, as the SAT problem is a
well-known NP-complete problem, it is also hard to deal when it comes to
realistic uses with huge formulas. Despite the rapid development of SMT solvers
in recent years, constraint solving remains one of the obstacles to achieve the
scalability for real-world crypto systems.
